Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-04-29 doc/manuscript/manuscript.Rmd
Added some cleaned up contrast functions to the main R folder that I can use to analyze the lists of linear/mixed models.

Phenotypic traits were analysed with a linear model with the form:

$$y_{ijk} = \mu + L_i + B(L_i) + G_k + GL_{ik} + \epsilon_{ijk}$$

Where $y_{ijk}$ is the phenotypic measurement for rep$j$ of genotype $k$ in environment $i$, $L_i$ is the effect of location $i$, $G_k$ is the effect of genotype $G$, $GL_{ik}$ is the interaction effect of location $L$ and genotype $G$, and $\epsilon_{ijk}$ is the measurement error.

Models were fit using the lm function in R[@rcoreteamLanguageEnvironmentStatistical2022], and analysis of variance (ANOVA) performed using the anova function. Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R. Least-significant difference values for each trait were calculated using the LSD.test function from the agricolae[@de2014agricolae] package. Pearson correlation coefficients between each phenotype were calculated with the cor function in R.

>>>>

Phenotypic traits were analysed with a mixed effects model with the form:

$$y_{ijk} = \mu + E_i + B(E_i) + G_k + GE_{ik} + \epsilon_{ijk}$$

Where $y_{ijk}$ is the phenotypic measurement for rep$j$ of genotype $k$ in environment $i$, $E_i$ is the effect of environment $i$, $B(E_i)$ is the effect of replication nested within environment, $G_k$ is the effect of genotype $G$, $GE_{ik}$ is the interaction effect of environment $E$ and genotype $G$, and $\epsilon_{ijk}$ is the measurement error. The genotype effect was treated as fixed and all other factors were treated as random.

Models were fit using the gamem_met function from the metan package[@olivotoMetanPackageMultienvironment2020]. Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R. The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL means to check means. Pearson correlation coefficients between each phenotype were calculated with the cor function in R.

### 2022-04-29 doc/manuscript/manuscript.tex
Added some cleaned up contrast functions to the main R folder that I can use to analyze the lists of linear/mixed models.

Phenotypic traits were analysed with a linear model with the form:

\[y_{ijk} = \mu + L_i + B(L_i) + G_k + GL_{ik} + \epsilon_{ijk}\]

Where \(y_{ijk}\) is the phenotypic measurement for rep\(j\) of genotype
\(k\) in environment \(i\), \(L_i\) is the effect of location \(i\),
\(G_k\) is the effect of genotype \(G\), \(GL_{ik}\) is the interaction
effect of location \(L\) and genotype \(G\), and \(\epsilon_{ijk}\) is
the measurement error.

Models were fit using the lm function in
R\citep{rcoreteamLanguageEnvironmentStatistical2022}, and analysis of
variance (ANOVA) performed using the anova function. Least-square means
(LS Means) for each genotype and trait were calculated using the above
model using the emmeans package\citep{lenthEmmeansEstimatedMarginal2022}
in R. Least-significant difference values for each trait were calculated
using the LSD.test function from the agricolae\citep{de2014agricolae}
package. Pearson correlation coefficients between each phenotype were
calculated with the cor function in R.

>>>>

Phenotypic traits were analysed with a mixed effects model with the
form:

\[y_{ijk} = \mu + E_i + B(E_i) + G_k + GE_{ik} + \epsilon_{ijk}\]

Where \(y_{ijk}\) is the phenotypic measurement for rep\(j\) of genotype
\(k\) in environment \(i\), \(E_i\) is the effect of environment \(i\),
\(B(E_i)\) is the effect of replication nested within environment,
\(G_k\) is the effect of genotype \(G\), \(GE_{ik}\) is the interaction
effect of environment \(E\) and genotype \(G\), and \(\epsilon_{ijk}\)
is the measurement error. The genotype effect was treated as fixed and
all other factors were treated as random.

Models were fit using the gamem\_met function from the metan
package\citep{olivotoMetanPackageMultienvironment2020}. Least-square
means (LS Means) for each genotype and trait were calculated using the
above model using the emmeans
package\citep{lenthEmmeansEstimatedMarginal2022} in R. The emmeans
package was also used to calculate contrasts as a post-hoc test to
compare RIL means to check means. Pearson correlation coefficients
between each phenotype were calculated with the cor function in R.
